\chapter*{Acknowledgements}
\graphicspath{{Figures/Common/}}

% People to thank:
% Supervisor/s: Joe Hope, Craig Savage, John Close.
% Family
% Friends
% Colleagues / coworkers: Julien Dugué, Oliver Topic, Justin Schultz, Simon Haine, Mattias Johnsson, Matthew Jeppesen, Sven Abend, André de Carvalho, Paul Altin, John Debs, Rachel Poldy, Ben Buchler, Stuart Szigeti, Robin Stevenson, Michael Hush, Daniel Döring, Gordon McDonald, Finn Lattimore, Kate Wagner, Jean-François Morizur, Mahdi Housseni, Nick Robins, Cristina Figl, Paul Summers

% Olympiad people for keeping me sane.  Mainly Kate, Matt & Alix. & Lucy

% An institution that will remain nameless for demonstrating the meaning of incompetence.

% Dave Singleton for not yelling at me too much when I managed to crash a supercomputer.

% People I have collaborated with with: Matt Davis, Andrew Truscott, Rob Dall

%I'd like to thank John for the endless games of hide-and-seek played in the last week.

% Proof-readers: John, Joe, Cristina, Mattias, Stuart, Robin, Michael, Rob.

% I would like to thank my lucky stars, and the cat, for not eating me.

First and foremost, I would like to thank my supervisors: Joe, John and Craig.  I have learnt much these past few years, and that could not have happened without your guidance.  

My supervisors have been invaluable in the writing of this thesis, as have my other proof-readers: André, Cristina, Daniel, Mattias, Michael, Rob, Robin, and Stuart.

I have had many interesting and enlightening discussions with people too numerous to count, but I must particularly thank Nick for his endless patience explaining the goings on of experimental physics, and Mattias \& Simon for teaching me the tricks with performing numerical simulations.

Over the past several years, I have had the great pleasure to work with an incredible group of people in the Physics Olympiad program.  In particular, I would like to thank Kate, Matt, Alix \& Lucy.  Who could ever thought it was possible to have fun while writing an exam?  As strange as it sounds, you have helped keep me sane.

Throughout my PhD, I have collaborated closely with the Rubidium and Helium BEC experimental groups at the ANU.  In particular, I would like to thank John, Nick \& Cristina from the Rubidium group and Andrew \& Rob from the Helium group for helping me learn the `language' of experimental physics.

I would like to thank the many people with whom I have shared my time at the `department of many names': André, Ben, Cristina, Daniel, Emily, Finn, Gordon, JD, Jean-François, Julien, Justin, Kate, Mahdi, Matthew, Mattias, Michael, Nick, Oliver, Paul~A., Paul~S., Rachel, Robin, Simon, Stuart, Sven and Tom.  You have been excellent company.  In time, perhaps, I can repay my debt of baked goods and chocolate.

Finally, I would like to thank my parents Greg \& Lynda.  You have encouraged me to delve into the nature of things, and to seek the satisfaction of understanding.