\chapter{Conclusion}
\label{Conclusion}
\graphicspath{{Figures/Conclusion/}{Figures/Common/}}

Atom lasers show extraordinary promise.  Using atoms instead of photons for interferometric measurements potentially increases the sensitivity by up to 10 orders of magnitude.  Although much of this gain is offset due to the much lower fluxes of available atomic sources, current atom interferometers are competitive or world-leading in the precision measurement of accelerations and rotations.  Coherent atomic sources (i.e.\ atom lasers) have fluxes even lower than the available thermal atomic sources that are used in current atom interferometers.  Coherent sources do, however, have two potentially significant advantages over thermal sources for atom interferometry.

The first is their narrower linewidth, and therefore velocity spread.  This enables more efficient operation of large momentum-transfer processes (which are highly velocity selective).  Large momentum-transfer processes are important for increasing the interaction time of the atoms, and therefore the phase shift to be measured.  Also, for larger interaction times the expansion of the atomic source increases signal loss \citep{Dimopoulos:2007uq}, an effect which is reduced by the use of a condensed source.

The second advantage of coherent sources is their potential for producing squeezed and entangled atomic sources.  In the context of quantum optics, squeezing has been used to reduce the shot noise limit (the standard quantum limit $\propto 1/\sqrt{N}$ where $N$ is the number of particles observed) in precision measurement by about a factor of 10.\footnote{FIXME: Missing citations.}  This is equivalent to an increase in the flux of the source of a factor of 100.  Entanglement has the possibility of even more dramatic improvements, however it relies on the creation of very fragile entangled sources.  The best that has been achieved in the context of quantum optics are entangled sources containing less than 10 photons \citep{Leibfried:2004}.  In the context of atom optics, squeezed atomic sources offer the possibility of increasing measurement sensitivity, while entangled sources are of greater interest for fundamental tests of quantum mechanics.

Atom lasers, as a technology, are still in their infancy.  The first pulsed atom lasers were demonstrated in 1997, and since then researchers have extracted them from condensates quasi-continuously, guided them, split them, and probed condensates with them.  They are an atomic analogue of the photon laser, except in one respect: they are not truly continuous.  When the condensate runs out of atoms, the atom laser stops.  Present-day atom lasers are more analogous to a leaky cavity than a laser in this respect.  

Creating a truly continuous coherent source for atoms is tricker than for photons.  Perhaps the largest challenge is that atom number is conserved.  It is not simply possible, by adding more energy to the system, to create additional atoms (at least not without adding a \emph{lot} of energy) as it is for photons.  A source of atoms is necessary to produce a truly continuous atom laser, and a mechanism is needed to replenish the condensate using this source, and the replenishment process must operate without significantly disturbing the coherence properties of the condensate.  It is this replenishment or pumping process that we have investigated theoretically in this thesis.

We have investigated two different pumping processes.  The first, considered in \chapterref{OpticalPumping}, was driving the system optically, using the emission of photons to make the pumping process irreversible.  This process has the advantage that atoms are not necessarily lost in the evaporation process, potentially making the pumping process highly efficient.  In an experimental realisation of this scheme using a condensate as the source, a 35\% efficiency for this transfer process was observed.  The flux of this particular realisation, however, would be limited by the rate at which the source condensates can be produced.  The interesting property of this system, however, is that following a detailed comparison of the theoretical and experimental results, there is some intriguing evidence that the harmful reabsorption processes in the experiment may be suppressed due to a quantum-mechanical interference effect.  A better theoretical understanding of this process could enable the source condensate to be replaced with a thermal source.  If possible, this would greatly increase the potential flux of the produced atom laser, creating a competitive coherent atomic source for atom interferometry.

A second, evaporatively-driven pumping process was considered in \chapterref{KineticTheory}.  



This pumping process is supplied by a thermal source, and could therefore have a higher flux than the optical pumping process supplied by condensates.


This pumping process 


This pumping process is supplied by a thermal source, and therefore could have a higher flux than the optical pumping process considered in \


This pumping process is supplied by a thermal source and therefore it could be possible for it to provide a condensed source of atoms at a similar flux to the thermal source.  However, the actual flux is necessarily lower as the evaporation process removes atoms from the system as part of the pumping mechanism.  One of the aims of \chapterref{KineticTheory} was to determine just how much lower the flux of the condensed source would be.  It was found that the largest flux achievable from an available thermal atomic source was $\sim\unit[10^5]{s\textsuperscript{-1}}$ at an efficiency of 0.05\%.

The second pumping process considered




it is more clear that they can operate with thermal sources, the question being more one of just how cold they must be for useful operation.

The evaporatively-driven pumping mechanism considered in \chapterref{KineticTheory}, is supplied by a thermal source and therefore it could be possible for it to provide a condensed source of atoms at a similar flux to the thermal source.  However, the actual flux is necessarily lower as the evaporation process removes atoms from the system as part of the pumping mechanism.  One of the aims of \chapterref{KineticTheory} was to determine just how much lower the flux of the condensed source would be.  It was found that the largest flux achievable from an available thermal atomic source was $\sim\unit[10^5]{s\textsuperscript{-1}}$, an average flux that is also achievable by producing independent condensates.





Although present atom interferometers are white-light interferometers that are independent of the de Broglie wavelength of the source, not all interferometer designs have this property.  All other things equal, it is a desirable property to have as it reduces fluctuations in the measurement due to errors in the de Broglie wavelength of the atoms, however there are surely other quantities that can only be measured with interferometers whose measured phase does depend on the wavelength of the atoms.  For these measurements, coherent sources of atoms will be the only available choice.

In this thesis, we have investigated one path to improving the utility of the atom laser: increasing its flux.

We have investigated this option in two different directions.  The first was driving the system optically, using sponteaneously emitted photons to make the pumping process irreversible.  This process has the advantage that atoms are not necessarily lost in the evaporation process, potentially making for a high-efficiency conversion of source atoms into the condensate.  In an experimental realisation of this scheme, a 35\% efficiency for this transfer process was observed.  This is much higher than that for the evaporation-driven process considered in the following process, in which the highest-flux atom laser produced with a real thermal source had an efficiency of 0.05\%.  With the process to evaporation understood, this could potentially be further improved by considering optimisations to the experiment proposed in that chapter.



Atom lasers are still a new technology.  



Atom lasers are still a new tool.  First developed in blah blah, 















The coherent atomic sources considered in this thesis cannot compete with the flux of present thermal sources.  They do, however, have two potentially significant advantages over thermal sources for atom interferometry.

The first is their narrower linewidth, and therefore velocity spread.  This enables more efficient operation of large momentum-transfer processes (which are highly velocity selective).  Large momentum-transfer processes are important for increasing the interaction time of the atoms, and therefore the phase shift to be measured.  Also, for larger interaction times the expansion of the atomic source increases signal loss \citep{Dimopoulos:2007uq}, an effect which is reduced by the use of a condensed source.

The second advantage of coherent sources is their potential for producing squeezed and entangled atomic sources.  In the context of quantum optics, squeezing has been used to reduce the shot noise limit (the standard quantum limit $\propto 1/\sqrt{N}$ where $N$ is the number of particles observed) in precision measurement by about a factor of 10\footnote{FIXME: Missing citations.}.  This is equivalent to an increase in the flux of the source of a factor of 100.  Entanglement has the possibility of even more dramatic improvements, however it relies on the creation of very fragile entangled sources.  The best that has been achieved in the context of quantum optics are entangled sources containing less than 10 photons \citep{Leibfried:2004}.  In the context of atom optics, squeezed atomic sources offer the possibility of increasing measurement sensitivity, while entangled sources are of greater interest for fundamental tests of quantum mechanics.

For the optical pumping mechanism considered in \chapterref{OpticalPumping}, the achievable flux of the atom laser is limited by the rate at which condensates can be produced to replace the source condensate as it is depleted.  Even if all of the atoms were transferred to the lasing condensate with perfect efficiency, the continuous atom laser produced could never exceed the average flux with which the source condensates can be produced.  The interesting property of this system, however, is that there is some intriguing evidence that the harmful reabsorption processes in that experiment may be suppressed due to a quantum-mechanical interference effect.  A better theoretical understanding of this process could enable the source condensate to be replaced with a thermal source.  If possible, this would greatly increase the potential flux of the produced atom laser, creating a competitive coherent atomic source for atom interferometry.

The evaporatively-driven pumping mechanism considered in \chapterref{KineticTheory}, is supplied by a thermal source and therefore it could be possible for it to provide a condensed source of atoms at a similar flux to the thermal source.  However, the actual flux is necessarily lower as the evaporation process removes atoms from the system as part of the pumping mechanism.  One of the aims of \chapterref{KineticTheory} was to determine just how much lower the flux of the condensed source would be.  It was found that the largest flux achievable from an available thermal atomic source was $\sim\unit[10^5]{s\textsuperscript{-1}}$, an average flux that is also achievable by producing independent condensates.

While neither of the proposed pumped atom lasers in their present forms would be competitive with thermal sources for atom interferometry, pumping could improve other atom laser experiments.  In particular, experiments in which squeezing or entanglement of atomic beams is being produced and measured.  In these experiments, the atomic beam will be condensed as it would be more difficult to detect squeezing or entanglement with a thermal source.  For these experiments, a pumped atom laser could potentially offer a narrower linewidth, increased flux, and continuous operation, all of which would increase the sensitivity of measurements of atomic squeezing and entanglement.

\chapterref{Peaks} discussed one such process that leads to the formation of entangled atomic beams.  Although in the experiment discussed in that chapter it would only be possible to measure number-difference squeezing and correlations in atom detection events, a different experiment was proposed in which it may be possible to measure the entanglement of the produced atomic beams.  This chapter has also demonstrated the excellent agreement that is achievable between theory and experiment for BEC systems.  This is possible due to extraordinary degree of control over external noise sources that is possible in experiments, and the effectiveness of the theoretical techniques available for modelling them.

\parasep

This thesis documents the work of a theorist working, for the most part, in close collaboration with experimentalists.  This is particularly evident in \chapterref{Peaks} and \chapterref{OpticalPumping}, but it is also true for other work not documented here.  I have attempted to resolve the minor mysteries that sometimes arise in experimental physics by working closely with the experimentalists as they are discovered, cause confusion, and for the most part, resolved.

% Now for a strong finish.


% Contrary to what has been expected previously, this chapter has demonstrated that optical pumping of an atom laser is feasible without making the condensate so narrow as to make it essentially transparent in at least one dimension.  The next step in the investigation of this pumping process must be the theoretical consideration of the potential positive contribution of reabsorption.  When this is better understood, consideration can then be given to the integration of the pumping mechanism with a method for replacing the source condensates to produce a continuously pumped atom laser.



