\chapter{Elementary excitations of temporally periodic Hamiltonians}
\label{PeaksAppendix}
\graphicspath{{Figures/PeaksAppendix/}{Figures/Common/}}

The theory of elementary excitations in unstable Bose-Einstein Condensates has been considered before \citep{Leonhardt:2003}. In this appendix, the methods discussed in \citep{Leonhardt:2003} will be applied to the case of temporally periodic but spatially homogeneous and isotropic Hamiltonians. One such Hamiltonian is obtained by making a perturbative expansion of the Hamiltonian \eqref{Peaks:InitialHamiltonian} considered in \sectionref{Peaks:PerturbativeApproach} about the time-dependent (but periodic) mean-field.

Consider a general quadratic Hamiltonian $\hat{H}(t)$ of period $T$ in terms of the operators $\hat{\phi}_i(\bm{x}, t)$ which obey the usual equal-time bosonic commutation relations. As the Hamiltonian $\hat{H}(t)$ is homogenous by assumption, the operator equations of motion will take their simplest form in a Fourier basis. In this basis the equations of motion for the operators $\hat{\phi}_i(\bm{k}, t)$ can be written in matrix form\footnote{FIXME: Probably need to add the argument that the Fourier transform must be of this form. It is simply a momentum conservation argument.},
\begin{subequations}
    \label{PeaksAppendix:MatrixOperatorEvolution}
    \begin{align}
        i \hbar \frac{\partial \hat{\bm{\Upsilon}}(\bm{k}, t)}{\partial t} &= \mathcal{H}(\bm{k}, t) \hat{\bm{\Upsilon}}(\bm{k}, t),\\
        \hat{\bm{\Upsilon}}(\bm{k}, t) &= 
        \begin{pmatrix}
            \hat{\phi}_1(\bm{k}, t) &
            \hat{\phi}_1^\dagger(-\bm{k}, t) &
            \hat{\phi}_2(\bm{k}, t) &
            \hat{\phi}_2^\dagger(-\bm{k}, t) &
            \dots
        \end{pmatrix}^T,
    \end{align}
\end{subequations}
where the matrix $\mathcal{H}(\bm{k}, t)$ obeys
\begin{align}
        \mathcal{H}(\bm{k}, t+T) &= \mathcal{H}(\bm{k}, t),\\
        \mathcal{H}(\bm{k}, t) &= \mathcal{H}(-\bm{k}, t), \label{PeaksAppendix:HReflectionSymmetry}
\end{align}
where the last equality holds because $\hat{H}(t)$ is isotropic.

If the Hamiltonian $\hat{H}(t)$ were not time-dependent, it could be diagonalised to find the (potentially complex) eigenvalues $\Omega_j(\bm{k})$ and corresponding operators $\hat{Q}_j(\bm{k}, t)$ which would evolve as
\begin{align}
    \label{PeaksAppendix:ContinouousTimeEigenoperators}
    i \hbar \frac{\partial \hat{Q}_j(\bm{k}, t)}{\partial t} &= \hbar \Omega_j(\bm{k}) \hat{Q}_j(\bm{k}, t),
\end{align}
where the $\hat{Q}_j(\bm{k}, t)$ need not obey boson commutation relations.

In the case of a periodic matrix $\mathcal{H}(\bm{k}, t)$ it is instead the monodromy matrix $\mathcal{M}(\bm{k})$ (see \sectionref{Peaks:FloquetsTheorem}) that we wish to diagonalise. The monodromy matrix $\mathcal{M}(\bm{k})$ satisfies
\begin{align}
    \label{PeaksAppendix:MonodromyMatrix}
    \hat{\bm{\Upsilon}}(\bm{k}, nT) &= \mathcal{M}(\bm{k})^n \hat{\bm{\Upsilon}}(\bm{k}, 0),
\end{align}
where $n$ is a positive integer. In place of \eqref{PeaksAppendix:ContinouousTimeEigenoperators} we seek the operators $\hat{Q}_j(\bm{k}, t)$ that obey
\begin{align}
    \label{PeaksAppendix:QOperatorEvolution}
    \hat{Q}_j(\bm{k}, T) &= \lambda_j(\bm{k}) \hat{Q}_j(\bm{k}, 0),
\end{align}
where the $\hat{Q}_j(\bm{k}, t)$ are defined by
\begin{align}
    \label{PeaksAppendix:QOperatorDefinition}
    \hat{Q}_j(\bm{k}, t) &= \bm{c}_j^\dagger(\bm{k}) \hat{\bm{\Upsilon}}(\bm{k}, t),
\end{align}
for some vectors $\bm{c}_j(\bm{k})$, where $\bm{c}_j^\dagger(\bm{k})$ denotes the conjugate transpose. 

Using definitions \eqref{PeaksAppendix:MonodromyMatrix}--\eqref{PeaksAppendix:QOperatorDefinition}, it follows that the $\lambda_j(\bm{k})$ and $\bm{c}_j^\dagger(\bm{k})$ are respectively the eigenvalues and left eigenvectors of $\mathcal{M}(\bm{k})$,
\begin{align}
    \hat{Q}_j(\bm{k}, T) &= \bm{c}_j^\dagger(\bm{k}) \hat{\bm{\Upsilon}}(\bm{k}, T) = \bm{c}_j^\dagger(\bm{k}) \mathcal{M}(\bm{k}) \hat{\bm{\Upsilon}}(\bm{k}, 0) = \lambda_j(\bm{k}) \bm{c}_j^\dagger \hat{\bm{\Upsilon}}(\bm{k}, 0) = \lambda_j(\bm{k}) \hat{Q}_j(\bm{k}, t).
\end{align}

The operators $\hat{Q}_j(\bm{k}, t)$ are not necessarily bosonic annihilation or creation operators. To determine the conditions under which they are, we consider their Hermitian conjugates $\hat{Q}_j^\dagger(\bm{k}, t)$. As every operator in $\hat{\bm{\Upsilon}}(-\bm{k}, t)$ is the Hermitian conjugate of an operator in $\hat{\bm{\Upsilon}}(\bm{k}, t)$, the $\hat{Q}_j^\dagger(\bm{k}, t)$ can be written as
\begin{align}
    \label{PeaksAppendix:QDaggerDefinition}
    \hat{Q}_j^\dagger(\bm{k}, t) &= \bm{d}_j^\dagger(\bm{k}) \hat{\bm{\Upsilon}}(-\bm{k}, t)
\end{align}
for some vectors $\bm{d}_j(\bm{k})$. It follows from \eqref{PeaksAppendix:QOperatorEvolution} that the $\hat{Q}_j^\dagger(\bm{k}, t)$ will obey
\begin{align}
    \label{PeaksAppendix:QDaggerEvolution}
    \hat{Q}_j^\dagger(\bm{k}, T) &= \lambda_j^*(\bm{k}) \hat{Q}_j^\dagger(\bm{k}, 0).
\end{align}

The commutators of the $\hat{Q}_j^{(\dagger)}(\bm{k}, t)$ will be constant as they are constant linear combinations of the $\hat{\phi}^{(\dagger)}(\pm\bm{k}, t)$, the commutators of which are themselves constant. Using this requirement gives
\begin{align}
    \left[ \hat{Q}_i(\bm{k}, T),\, \hat{Q}_j^\dagger(\bm{k}, T) \right] &= \left[ \lambda_i(\bm{k}) \hat{Q}_i(\bm{k}, 0),\, \lambda_j^*(\bm{k}) \hat{Q}_j^\dagger(\bm{k}, 0)\right]\\
        &= \lambda_i(\bm{k}) \lambda_j^*(\bm{k}) \left[ \hat{Q}_i(\bm{k}, 0),\, \hat{Q}_j^\dagger(\bm{k}, 0)\right].
        \label{PeaksAppendix:InvariantCommutator}
\end{align}
For \eqref{PeaksAppendix:InvariantCommutator} to be true, either $\lambda_i(\bm{k}) \lambda_j^*(\bm{k}) = 1$ or the two operators commute. Specifically, for $\hat{Q}_i(\bm{k}, t)$ to be an annihilation or creation operator it is required that ${\lambda_i^*(\bm{k})}^{-1} = \lambda_i(\bm{k})$. In terms of the Floquet exponents (see \sectionref{Peaks:FloquetsTheorem}) $\displaystyle \xi_i(\bm{k}) = \frac{1}{T} \ln \lambda_i(\bm{k})$, this requirement becomes $\xi_i(\bm{k}) = i \omega_i(\bm{k})$. Hence it is only for purely imaginary Floquet exponents that the eigenvalues of $\mathcal{M}(\bm{k})$ correspond to bosonic annihilation or creation operators.

Generally, the Floquet exponents $\xi_i$ may have a non-zero real component. In this case the $\hat{Q}_i(\bm{k}, t)$ will not be bosonic annihilation or creation operators, although such operators can be constructed from linear combinations of the $\hat{Q}_i(\pm\bm{k}, t)$. Before constructing such operators, we first consider the restrictions on the possible eigenvalues of $\mathcal{M}(\bm{k})$.

First, it is noted that if $\lambda_i(\bm{k})$ is an eigenvalue of $\mathcal{M}(\bm{k})$, then from \eqref{PeaksAppendix:QDaggerDefinition}--\eqref{PeaksAppendix:QDaggerEvolution} $\lambda_i^*(\bm{k})$ must be an eigenvalue of $\mathcal{M}(-\bm{k})$. However, from the reflection symmetry of $\mathcal{H}(\bm{k})$ defined by \eqref{PeaksAppendix:HReflectionSymmetry} we have that $\mathcal{M}(-\bm{k}) = \mathcal{M}(\bm{k})$ and hence $\lambda_i^*(\bm{k})$ must also be an eigenvalue of $\mathcal{M}(\bm{k})$.

Secondly, not all of the operators $\hat{Q}_i^{(\dagger)}(\bm{k}, t)$ can commute. As the $\hat{Q}_i^{(\dagger)}(\bm{k}, t)$ form a complete basis, for every operator there must be at least one other operator with which it does not commute. From \eqref{PeaksAppendix:InvariantCommutator} then follows the requirement that if $\lambda_i(\bm{k})$ is an eigenvalue,   ${\lambda_i^*(\bm{k})}^{-1}$ must also be an eigenvalue.



\section{References to this appendix}

The normalised eigenvectors of the system are not always annihilation or creation operators; as is discussed in \appendixref{PeaksAppendix}, this is only true when the Floquet exponents are pure imaginary. When the Floquet exponents have a nonzero real component, annihilation and creation operators can be constructed from linear combinations of the eigenvectors. Not being eigenvectors, these operators will therefore have nontrivial evolution. As is shown in \appendixref{PeaksAppendix}, Floquet exponents with nonzero real parts come in pairs of the form $\pm \gamma(\bm{k}) + i \omega(\bm{k})$. From the corresponding eigenvectors to these Floquet exponents the bosonic annihilation operator $\hat{\Lambda}(\bm{k}, t)$ can be formed, which evolves as
\begin{align}
    \label{Peaks:DynamicalInstability}
    \hat{\Lambda}(\pm\bm{k}, nT) &= e^{\pm i n\omega T} \left( \sinh(n\gamma T) \hat{\Lambda}^\dagger(\mp\bm{k}, 0) + \cosh(n\gamma T) \hat{\Lambda}(\pm\bm{k}, 0)\right),
\end{align}
where $n$ is a positive integer. Due to the exponential growth in \eqref{Peaks:DynamicalInstability}, the mode corresponding to $\hat{\Lambda}(\bm{k})$ represents a dynamical instability of the condensate.
